Relational Presentations Using Semantic Closeness\\Spatial Narrative for Mathematical Content

### 2015-06-13 Paper.tex
addressed Review 2 comment 2

We will now commence the journey towards building a more effective presentation format to improve knowledge transfer in Mathematics by allowing flexibility in presentations. In the following we will assume the reader is familiar with OMDoc \cite{Kohlhase:OMDoc1.2} and with the open-source presentation framework \textit{impress.js} \cite{JSImpress:npentrel14} which will be used to create the final presentation in the form of an interconnected network of information that tells a visual story based on semantic closeness to facilitate the transfer of knowledge. To create these presentations automatically, the tool \sys \cite{npentrel:npentrel15} was created.

>>>>

We will now commence the journey towards building a more effective presentation format to improve knowledge transfer in Mathematics by allowing flexibility in presentations. In the following we will use OMDoc \cite{Kohlhase:OMDoc1.2} and the open-source presentation framework \textit{impress.js} \cite{JSImpress:npentrel14} which will be used to create the final presentation in the form of an interconnected network of information that tells a visual story based on semantic closeness to facilitate the transfer of knowledge. The paper will point out some functions of OMDoc as needed; the interested reader is encouraged to explore OMDoc in the cited paper. JSImpress merely serves for visualization, further understanding of the tool is not needed for the purpose of the paper. To create these presentations automatically, the tool \sys \cite{npentrel:npentrel15} was created.
